---
output: pdf_document
params: 
  data: ""
  id: ""
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

cars <- params$data
car_name <- params$id
car <- filter(cars, car == car_name)

```

# Report for: `r car_name`
This report is a example to showcase how roosdorp::generate_report() can be used to generate a large amount of reports from a user inputted data set.

## Introduction
This report aims to provide a thorough analysis of the performance of the `r car_name` car model in terms of fuel efficiency and power. The data was obtained from the `mtcars` data set and it will be analyzed using descriptive statistics and visualization techniques.

## Descriptive Statistics
The `r car_name` has `r car$cyl` cylinders and an output of `r car$hp` horsepower. It weighs `r car$wt` tons and has a fuel efficiency of `r car$mpg` miles per gallon (MPG). These values are consistent with the trend in the market, where cars with more cylinders and higher horsepower tend to have lower fuel efficiency.

## Visualization
A scatter plot is created to visualize the relationship between the number of cylinders and horsepower on one hand and the fuel efficiency (MPG) on the other hand. The `r car_name` is represented by a red dot on the plot. As seen in the scatter plot, there is a clear negative correlation between the number of cylinders and horsepower and the fuel efficiency (MPG).

```{r Plot}
ggplot(cars, aes(x = mpg, y = hp, size = cyl, color = cyl)) +
  geom_point(alpha = 0.7) +
  labs(title = car_name,
       size = "Cylinders") +
  xlab("Horsepower") +
  ylab("MPG (Miles per gallon)") +
  geom_point(data = car, aes(x = mpg, y = hp), size = 5, color = "red", alpha = 0.7)
```
